Assumptions of Physics overview: \\ Quantum mechanics and irreducibility

### 2021-10-10 Overviews/Quantum mechanics/QuantumMechanicsOverview.tex
Overviews: updating revtex4 reference
Overviews: final pass to quantum mechanics

\documentclass[10pt,twocolumn, nofootinbib]{revtex4-1}
%\documentclass[aps,pra,10pt,twocolumn,floatfix,nofootinbib]{revtex4-1}
%\documentclass[10pt,twocolumn,letterpaper]{article}

@@

\begin{abstract}
We briefly show how quantum mechanics can be rederived and better understood as a consequence of irreducibility. The Schroedinger equation (i.e. unitary evolution) is recovered as deterministic and reversible motion while the measurement process is recovered as a special case of a process with equilibria (i.e. idempotent process, projection).  This work is an overview of some of the results of Assumptions of Physics, a project that aims to identify a handful of physical principles from which the basic laws can be rigorously derived  (\url{https://assumptionsofphysics.org}).
\end{abstract}

@@

The overall argument (see \cite{AoPPhy1,AoPBook} for more details) can be summed up in the following diagram that can be used as a guide throughout this note.

@@

Let $\mathcal{C}$ be the state space of the irreducible system. Let us call fragment a part of the irreducible system. The state of a fragment will be associated with a random variable uniformly distributed over the possible fragment states. As discussed in the context of classical mechanics(CITE), distributions over states must be invariant and symplectic manifolds are the only manifolds over which invariant distributions can be defined. As we cannot say anything about the state of the fragments, the dimensionality of this manifold must be irrelevant as long as it is even dimensional. For simplicity, we can choose a two-dimensional one. Therefore we are interested in the space of bi-dimensional uniform distributions formed by a pair of two random variables $A$ and $B$.

>>>>

\documentclass[10pt,twocolumn, nofootinbib]{revtex4-2}
%\documentclass[aps,pra,10pt,twocolumn,floatfix,nofootinbib]{revtex4-1}
%\documentclass[10pt,twocolumn,letterpaper]{article}

@@

\begin{abstract}
We briefly summarize our strategy to understand and rederive quantum mechanics as a consequence of irreducibility. The Schroedinger equation (i.e. unitary evolution) is recovered as deterministic and reversible motion while the measurement process is recovered as a special case of a process with equilibria (i.e. idempotent linear process, projection).
\end{abstract}

@@

The ideas and result summarized here are part of our larger project Assumptions of Physics (see \cite{AoPPhy1,AoPBook} for more details). They represent the current best understanding and will be revised as the project matures.

This note can be summed up in the following diagram that can be used as a guide throughout this note.

@@

Let $\mathcal{C}$ be the state space of the irreducible system. Let us call fragment a part of the irreducible system. The state of a fragment will be associated with a random variable uniformly distributed over the possible fragment states. As we show in the context of classical mechanics, distributions over states must be invariant and symplectic manifolds are the only manifolds over which invariant distributions can be defined. As we cannot say anything about the state of the fragments, the dimensionality of this manifold must be irrelevant as long as it is even dimensional. For simplicity, we can choose a two-dimensional one. Therefore we are interested in the space of bi-dimensional uniform distributions formed by a pair of two random variables $A$ and $B$.\footnote{We are looking into alternative strategies for this part, as we are not fully satisfied with it.}
